---
title             : "General Linear Model"
shorttitle        : "Dummy variable coding"

author: 
  - name          : "Your Name"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"

affiliation:
  - id            : "1"
    institution   : "Rutgers University"

author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

abstract: >
  Enter abstract here (note the indentation, if you start a new paragraph).
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

class             : "man"
output            : papaja::apa6_word
---


# Load libraries

Use this section to load the libraries you will use. 

```{r, 'load_libraries', echo=TRUE}
library("papaja")
library("tidyverse")
```


# Load data

Use this section to load the data you will use. 

```{r, 'load_data', echo=TRUE}


```


# Tidy data

Use this section to tidy your data so that it is in long format. 

```{r, 'tidy_data'}
# df_tidy <- 

```


# Descriptive statistics

Use this section to explore your data (`head()`, `tail()`, `psych::describe()`), 
and calculate descriptive statistics.

```{r, 'descriptives', echo=TRUE}


```



# Fit models

<!--
In the following sections you will fit your models. 
-->


## Fit a null model

```{r, 'mod_null'}
# mod_null <- lm()

```


## Add a categorical predictor



## Add a continuous covariate



## Include an interaction term



## Test main effects and interaction term



# Results

<!--
In this section you will write up your results. 
-->



## Model description



## Interpretation

<!--
you can check out `easystats::report()` if you want, but don't rely on it. 
https://github.com/easystats/report
-->





```{=openxml}
<w:p>
  <w:r>
    <w:br w:type="page"/>
  </w:r>
</w:p>
```

## About this document

We used the `tidyverse` [@R-tidyverse] for data manipulation and R [@R-base] for all our analyses. 
This document was prepared in RMarkdown using `papaja` [@R-papaja]. 


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
