---
title   : 'Statistics for Linguists'
subtitle: 'Day 1'
author  : "Joseph V. Casillas, PhD"
date    : "Rutgers University</br>Last update: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: assets
    css: ["hygge", "rutgers", "rutgers-fonts"]
    nature:
      beforeInit: ["https://www.jvcasillas.com/ru_xaringan/js/ru_xaringan.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
    includes:
      in_header: "../assets/partials/header.html"
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-extra-all-the-things, echo=FALSE}
xaringanExtra::use_xaringan_extra(
  c("tile_view", "panelset", "editable", "animate", "tachyons", "webcam")
)
```

```{r, 'helpers', echo=FALSE, message=F, warning=F}
source(here::here("slides", "assets", "scripts", "helpers.R"))
```

class: title-slide-section-grey, middle

# .white[Statistical thinking]

---
layout: true

# Statistical thinking

---

### A necessary evil

- Mastering quantitative methods is an "[...] increasingly vital component of linguistic training" (Johnson, 2008). 

--

- Main roadblock = lack of resources

--

- Most programs don't offer this training. Students get it elsewhere (or not at all)

--

- Not a lot of good texts made specifically for linguistics

--

  - "Linguists learn to do stats on the street."
  - "If you want to be a phonotician today, you really have to train to be a 
  programmer."
